---
title: "miguelvignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{miguelvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#### miguelcltb creates a random sample for a binomial distribution and creates histogram of sample means for the distribution.
```{r setup}
library(MATH4753rund0006)
MATH4753rund0006::miguelcltb(n=5,iter=10000,p=0.5)
```

#### mynorm function creates a graph of maximum likelihood from a normal distribution. First, it uses a vector to pass data through and then creates a range of means and standard deviations.
```{r}
library(MATH4753rund0006)
mynormfunction(x=c(5,7,7,8,10),mu=seq(5,10,length=1000),sig=seq(0.1,4,length=1000))
```

#### myboot2 creates a histogram of Bootstrap sample statistics. First you pass a vector of data through the x parameter and then call desired statistic you want to sample. Finally you put the confidence level in the alpha parameter.
```{r}
library(MATH4753rund0006)
myboot2(x=c(1,3,4,5,3,2), fun="mean", alpha=0.05)
```

#### scatterhist creates a scatterplot layered over a barplot, and was my first package back when I was still learning how to make packages. It passes 2 vectors of data through and plots them on an x and y axis. 
```{r}
library(MATH4753rund0006)
scatterhist(c(1,5,8,7),c(7,2,9,3),"x-axis","y-axis")
```
